Generating Images From Captions\\ With Attention

### 2015-10-27 supp.tex
spelling

The GAN model trained on residuals which was used for sharpening had the same configuration as the $28 \times 28$ model trained by \cite{denton_lapgan} on residuals of CIFAR dataset, that can be found at \url{https://gist.github.com/soumith/e3f722173ea16c1ea0d9}. The model was trained for $6$ epochs.

>>>>

The LAPGAN model used for sharpening had the same configuration as the $28 \times 28$ model trained by \cite{denton_lapgan} on the edge residuals of CIFAR dataset.  that can be found at \url{https://gist.github.com/soumith/e3f722173ea16c1ea0d9}. The model was trained for $6$ epochs.
